\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{fancyhdr}

% Geometry settings
\geometry{
    left=0.75in,
    right=0.75in,
    top=0.75in,
    bottom=0.75in
}

% Hyperlink Setup
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
    pdftitle={Rembrant Oyangoren Albeos - CV},
    pdfauthor={Rembrant Oyangoren Albeos}
}

% Formatting
\titleformat{\section}{\large\bfseries\uppercase}{}{0em}{}[\hrule]
\titlespacing{\section}{0pt}{12pt}{6pt}

\newcommand{\entry}[2]{
    \noindent\textbf{#1} \hfill #2 \\
}

\begin{document}

% --- Header ---
\begin{center}
    {\Huge \textbf{REMBRANT OYANGOREN ALBEOS}} \\[6pt]
    2025-2026 Unemployed, Algorithmic Trader, Software Programmer, Independent Researcher \\[4pt]
    ORCID \textbar{} Email \textbar{} Xcom \textbar{} GitHub
\end{center}

% --- Professional Summary / Lead ---
\section*{Experience}
\noindent \textbf{Lead, Founder \& CEO: WQ Wildmind Quasars LLC} \\
Total quantitative models’ tested fees: $\sim$ ₱245k accounting live trading days $n < 6$ months.

% --- Research ---
\section*{Research}

\textbf{SUM3API (Published at SSRN)} \\
\textit{Title:} “SUM3API: Using Rust, ZeroMQ, and MetaQuotes Language (MQL5) API Combination to Extract, Communicate, and Externally Project Financial Data from MetaTrader 5 (MT5)”. \\
The corresponding GitHub repository is at SUM3API, which consists of a complete end-to-end system architecture, MQL5-ZMQ wrapper \& Rust-ZMQ wrapper libraries covering the SUM3API system. Derived from the previous project at RustZMQMT5. 
\textit{(See Appendix A for Techstack)}

% --- Software ---
\section*{Software}

\textbf{QRAT2025 - Quantitative Research \& Algorithmic Trading} \\
Contains self-made (non AI) manual methodologies covering volume profile, tpo, footprint, heatmap, dom (orderflows) concepts, 360-page pdf. Projects combination of PineScript, MQL5, Python + JupyterNotebook. Models’ tested fees: $\sim$ ₱147k.
\textit{(See Appendix A for Techstack)}

\textbf{RustZMQMT5} (Jan 2026) \\
First to implement Rust + ZMQ + MT5’s MQL5 combination to exploit Bid/Ask live-trading data. Visualizing a simple orderflow developing in microseconds into a clean chart. Supported by survey responses from 9 AI-leading platforms.
\textit{(See Appendix A for Techstack)}

\textbf{MTParsee} (Jan 2026) \\
An MT5-trade-report.xlsx file parser that constructs statistical graphs (linechart and y-distribution) for clear visualization of the trading strategy performance. Handles 71,478-cell dataframe to generate 76 rolling trading metrics.
\textit{(See Appendix A for Techstack)}

\textbf{AiQG} (Jan 2026) \\
Webapp AiQuasarous Global built to make AI model exploration simple. Instantly access 284 AI platforms available worldwide for FREE, organized into 37 categories.
\textit{(See Appendix A for Techstack)}

\textbf{WNDRanking} (Dec 2025) \\
Fetches the latest National debt data, Debt as \% of GDP, and Debt per Capita from the World Population Review, and visualizes it using interactive plots, choropleth maps, and rank profiles.
\textit{(See Appendix A for Techstack)}

% --- Education ---
\section*{Education}

\entry{College at CIT-U - Electrical Engineering Student}{2024-2025}
\noindent Tuition fee: $\sim$ ₱85k. Reason: Passion for EE died, Conflict of Interest. \\
\textit{Most useful Tech I learned before I dropped out:} Autodesk’s Computer-aided design (CAD)

\entry{High School at ANHS - SSC \& STEM Student}{2018-2024}

% --- Other Research (High School/Earlier) ---
\section*{Earlier Research \& Projects}

\textbf{TB2024 - The Tindak Boltahe (Pedal Lightning)} \\
Project covering both hardware and software. Innovation focuses on the use of unstationary cycling to produce renewable electricity. Project worth ₱ 20,464.
\textit{(See Appendix A for Techstack)}

\textbf{Competition History}
\begin{itemize}[leftmargin=*]
    \item \textbf{June 2023:} GAD-Complaint Division Festival of Talents in Science-Stemazing. (DepEd Ecotech Center).
    \item \textbf{July 2023:} Regional Innovation Camp. (Philippine Science High School Central Visayas Campus).
\end{itemize}

\textbf{Head Project Creator Records}
\begin{itemize}[leftmargin=*]
    \item Consulted 12 groups in STEM at ANHS, with 7 approved research topics.
    \item Created a sturdy 7’4”x4’ Christmas 3-Face Pine Tree (plastic bottles/tin cans).
    \item Created a 6’2”x5’8” Christmas 12-Pointed Star (bamboo/indigenous materials).
\end{itemize}

% --- Others ---
\section*{Miscellaneous \& Skills}

\textbf{Others}
\begin{itemize}[leftmargin=*]
    \item Traditional/Digital drawings portfolio (47 items 2019-2020, 173 items 2020-2023).
    \item Author of \textit{MNI2023 Malamig na Init} on Wattpad.
    \item Champion Digital Poster (2021).
    \item Open-source manual trading strategies (Miro 2025).
    \item Born: September 6, 2005.
\end{itemize}

\textbf{Teamwork Skills} \\
I value team members and help them to elevate their individual skills. I prioritize shipping the solution to the problem rather than being a nerdy one.

\newpage
\appendix
\section*{Appendix A: Techstack and Applications Details}
\label{appendix:techstack}

% --- Appendix Comments Section content ---

\subsection*{Research: SUM3API}
\begin{itemize}
    \item \textbf{Techstack:} Git, Rust (eframe, egui, egui\_plot, zeromq, serde, serde\_json, tokio, futures, chrono), MetaQuotes Language 5 (MQL5) (mq5, mqh, dll), MQL4, ZeroMQ (ZMQ), Bat/Shell, LaTex \& BibTeX
    \item \textbf{Applications:} Git, Rust (w/ cargo), MetaTrader 5 (MT5), MetaEditor 5, Visual Studio C++ Build Tools, Windows PowerShell, ORCID, SSRN, Overleaf, Google Docs, Google Gemini Pro, Anthropic CaludeOpus4.5, Google Antigravity
\end{itemize}

\subsection*{Software: QRAT2025}
\begin{itemize}
    \item \textbf{Techstack:} pinescript, mql5 (C++), python (MetaTrader5, numpy, pandas, scikit-learn, scipy, pytz, datetime, plotlly, matplotlib, request, os, re, bs4, json, random, mplfinance, yfinance, geopandas, geodatasets, folium, cartopy), csv, tex
    \item \textbf{Applications:} TradingView, MetaTrader5, JupyterLab, GoCharting, Exness, Miro, GoogleDocs, GoogleSheets, Overleaf, Google Scholar, arXiv, GitHub, Codespace, OpenAI ChatGPT, Google Gemini Pro
\end{itemize}

\subsection*{Software: RustZMQMT5}
\begin{itemize}
    \item \textbf{Techstack:} Git, Rust (eframe, egui, egui\_plot, zeromq, serde, serde\_json, tokio, futures), MetaQuotes Language 5 (MQL5) (mq5, mqh, dll), MQL4, ZeroMQ (ZMQ), Bat/Shell
    \item \textbf{Applications:} Git, Rust (w/ cargo), MetaTrader 5 (MT5), MetaEditor 5, Visual Studio C++ Build Tools, Windows PowerShell, Google Gemini Pro, Google Antigravity
\end{itemize}

\subsection*{Software: MTParsee}
\begin{itemize}
    \item \textbf{Techstack:} Python (pandas, numpy, openpyxl, pathlib, os, plotly, scipy, watchdog, kaleido), xlsx, csv, png, pdf
    \item \textbf{Applications:} VisualStudio Code, Excel sheets, MetaTrader5, Google Gemini Pro
\end{itemize}

\subsection*{Software: AiQG}
\begin{itemize}
    \item \textbf{Techstack:} JavaScript (ReactJS, NodeJS), CSS, Git, HTML
    \item \textbf{Applications:} GitHub Codespace, Vercel, Microsoft Bing, Google Gemini Pro, OpenAI ChatGPT, Anthropic Claude AI
\end{itemize}

\subsection*{Software: WNDRanking}
\begin{itemize}
    \item \textbf{Techstack:} Python (requests, bs4, pandas, plotly, re)
    \item \textbf{Applications:} GitHub Codespace, Jupyter Lab, World Population Review, OpenAI ChatGPT
\end{itemize}

\subsection*{Research: TB2024 (Hardware/Software)}
\begin{itemize}
    \item \textbf{Techstack:} C++
    \item \textbf{Hardware:} Arduino UNO R3, Solar Panel, PC Fan Moto, Bottle Dynamo, Lithium Baterries, LCD 1602, IC Module, 5V Relay Module, HW-384, Trimmer potentiometer 10k resistor, Tactile Buttons, switches, Metal film Resistor, Diode 3A, Capacitor 2200uf 25V, Female and Male Adapter ports, PCB Board, jumper wires, Breadboard, RGB LEDs, Wire, Flat belt, Chain Clasp Connector, Electrical Tape, Road Bike Promax.
    \item \textbf{Applications:} Ardiono IDE, Thinkercad, Smart Draw Schematic Circuits
\end{itemize}

\subsection*{Other Applications Mentioned}
\begin{itemize}
    \item \textbf{General:} Autodesk Fusion360, GoogleDocs, PowerPoint, IbisPaintX
    \item \textbf{Explored:} MemReduct, SketchUP, Autodesk Fusion360, Autodesk CAD, IbisPaintX, Krita, Notion
\end{itemize}

\end{document}
